%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Benjamin Arnett} \\ \vspace{1pt}
    \small 571-598-0306 $|$ \href{mailto:benjaminarnett7@gmail.com}{\underline{benjaminarnett7@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/benjamin-arnett}{\underline{linkedin.com/in/benjamin-arnett}} $|$
    \href{https://github.com/benjaminarnett}{\underline{github.com/benjaminarnett}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {George Mason University}{Fairfax, VA}
      {Bachelor of Science in Information Technology, Concentration in Web App Development}{Aug. 2018 -- Dec. 2023}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Web Development Intern}{May 2023 -- August 2023}
      {Skywide Logic}{Newport Beach, CA}
      \resumeItemListStart
        \resumeItem{Collaborated with other interns to develop the business's website in WordPress CMS.}
        \resumeItem{Evaluated multiple API plugins for importing occupational data.}
        \resumeItem{Styled banner image and search field on home page.}
        \resumeItem{Diagnosed and resolved WordPress plugin update error by identifying and removing redundant plugin.}
        \resumeItem{Used hosting provider interface to create subdomain for test branch implementation.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\href{https://github.com/benjaminarnett/passphrase-gen}{\textbf{Passphrase Gen}} $|$ \emph{React, Node.js, Tailwind CSS}}{Jan. 2024}
          \resumeItemListStart
            \resumeItem{Passphrase Gen allows to generate a strong passphrase using common words.} 
            \resumeItem{Incrementing/decrementing word length and regeneration are performed with corresponding buttons.}
            \resumeItem{}{Displays passphrase strength (in bits of entropy) and average time to correctly guess the passphrase.}
            \resumeItem{Tailwind CSS utility classes are used to style margins and font size.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
    
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{GMU IT Senior Capstone} $|$ \emph{Home Assistant Operating System (YAML), Spiceworks}}{Jan. 2023 -- Dec. 2023}
          \resumeItemListStart
            \resumeItem{Our team was tasked with helping a local business improve their IT infrastructure. We automated customer notifications and configured an incident logging system.}
            \resumeItem{Automated notifications for smart TVs by setting triggers to execute at a specified time each day.}
            \resumeItem{Notifications include custom images, text, and sounds via YAML configuration.}
            \resumeItem{Enabled ticket creation and tracking using the Spiceworks Cloud Help Desk platform.}
            \resumeItem{Roles to enforce access privileges and categories to organize tickets were implemented to easily log incidents within the context of the client's business.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\href{https://github.com/benjaminarnett/shpd-website}{\textbf{Shattered Pixel Dungeon Website}} $|$ \emph{Bootstrap, jQuery, XMLHttpRequest}}{Aug. 2023 -- Dec. 2023}
          \resumeItemListStart
            \resumeItem{An enthusiast website built in dedication to the \emph{Shattered Pixel Dungeon} game as part of IT331, Web I: Web Development.}
            \resumeItem{Bootstrap default .container class was applied to make pages responsive.}
            \resumeItem{jQuery was used to validate form inputs and execute animations.}
            \resumeItem{On mouseover event, XMLHttpRequest was used to retrieve images.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\href{https://github.com/benjaminarnett/sqlite-editor}{\textbf{SQLite Editor}} $|$ \emph{Express.js, EJS, SQLite}}{Jan. 2023}
          \resumeItemListStart
            \resumeItem{Created web app that allows users to create, delete, and search SQLite databases.} 
            \resumeItem{Users are prompted to confirm their database deletion.}
            \resumeItem{Displayed databases are automatically filtered by search queries.} 
            \resumeItem{Provides routes to handle get/post requests with Express.js.} 
            \resumeItem{Enables the use of templates (i.e., header/footer) with EJS.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
    



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: JavaScript, SQL (SQLite), HTML/CSS, Python} \\
     \textbf{Frameworks}{: Create React App, Node.js, Tailwind CSS, Express.js, WordPress CMS} \\
     \textbf{Developer Tools}{: Git, VS Code} \\
     \textbf{Libraries}{: React}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
